PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-06 paper/sec-results.tex
Sect 3

In comparison to the PDF uncertainty, the size of the EW corrections is always
larger. We therefore anticipate that, once included in a PDF fit, they would
recast the relative weight of each data set included in the fit, and possibly
lead to an improvement in their overall description. In comparison to the scale
uncertainty, the size of the EW correction is similar, except on the Z-boson
mass peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, where the scale uncertainty exceeds
the size of the EW correction by about a factor of five. These facts confirm,
as expected, that EW corrections are almost immaterial at the Z-boson mass
peak, but that NNLO QCD corrections are otherwise as relevant as NLO QCD+EW
corrections. Finally, the Monte Carlo statistical uncertainty remains negligible
in comparison to the data, PDF and scale uncertainties, and to the size of the
EW correction, except for a couple of bins at forward rapidity in the highest
invariant mass bins. Improving the Monte Carlo precision will require to
generate a larger number of events, possibly with cuts that select
only the kinematic bins affected by the largest MC uncertainties. If this
turned out to be computationally too expensive, it would be desirable to treat
this uncertainty as an additional theoretical uncertainty in the PDF
fit~\cite{Ball:2018lag}.

>>>>

In comparison to the PDF uncertainty, the size of the EW corrections is always
larger. We therefore anticipate that, even if the agreement between the more
accurate theory (including EW corrections) and the data will remain the same,
the PDFs will however become overall more accurate. In comparison to the scale
uncertainty, the size of the EW correction is similar, except on the Z-boson
mass peak, $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$, where the scale uncertainty exceeds
the size of the EW correction by about a factor of five. These facts confirm,
as expected, that EW corrections are almost immaterial at the Z-boson mass
peak, but that NNLO QCD corrections are otherwise as relevant as NLO QCD+EW
corrections. Finally, the Monte Carlo statistical uncertainty remains negligible
in comparison to the data, PDF and scale uncertainties, and to the size of the
EW correction, except for a couple of bins at forward rapidity in the highest
invariant mass bins. Improving the Monte Carlo precision will require to
generate a larger number of events, possibly with cuts that select
only the kinematic bins affected by the largest MC uncertainties. If this
turned out to be computationally too expensive, it would be desirable to treat
this uncertainty as an additional theoretical uncertainty in the PDF
fit~\cite{Ball:2018lag}.
